Sparse Function-space Representation \\ of Neural Networks

### 2023-05-15 paper/main.tex
Captions

% Our method
\newcommand{\our}{DNN2SGP\xspace}

@@

  \end{tikzpicture}
  \newcommand{\mycircle}{\protect\tikz[baseline=-.5ex]\protect\node[circle,inner sep=2pt,draw=black,fill=C0,opacity=.5]{};}
  \newcommand{\mysquare}{\protect\tikz[baseline=-.5ex]\protect\node[inner sep=2.5pt,draw=black,fill=C1,opacity=.5]{};}
  %
  \caption{Binary classification (\mysquare~vs.~\mycircle) on the {\sc banana} toy data data set. We convert the left-hand neural network  }
  \label{fig:banana}  
\end{figure}

>>>>

% Our method
\newcommand{\our}{{\sc dnn2sgp}\xspace}

@@

  \end{tikzpicture}
  \newcommand{\mycircle}{\protect\tikz[baseline=-.6ex]\protect\node[circle,inner sep=2pt,draw=black,fill=C0,opacity=.5]{};}
  \newcommand{\mysquare}{\protect\tikz[baseline=-.6ex]\protect\node[inner sep=2.5pt,draw=black,fill=C1,opacity=.5]{};}
  \newcommand{\myinducing}{\protect\tikz[baseline=-.7ex]\protect\node[circle,inner sep=1.5pt,draw=black,fill=black]{};}
  %
  \caption{\textbf{Uncertainty quantification} for binary classification (\mysquare~vs.~\mycircle). We convert the trained neural network (left) to a sparse GP model that summarizes all data onto a sparse set of inducing points~\myinducing\ (middle). This gives similar behaviour as would running full Hamiltonian Monte Carlo (HMC) on the original neural network model weights (right). Marginal uncertainty depicted by colour intensity.\looseness-1}
  \label{fig:banana}  
\end{figure}
